---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Identify spikes in repeated measures of symptoms

<!-- badges: start -->
<!-- badges: end -->

Working together with Asha Ladwa on code for identifying (depression) symptom spikes.
This is currently work in progress and will eventually be moved to Asha's [GitHub](https://github.com/AshaLadwa) account.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("milanwiedemann/symptomspikes")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(symptomspikes)
library(tidyverse)
```

# Identify spikes

- See the help file for more information `help(identidy_spikes)`

```{r}
# Define a list of repeated measures to be checked for depression spikes
phq_variables <- c("phq_1", "phq_2", "phq_3", "phq_4", 
                   "phq_5", "phq_6", "phq_7", "phq_8", 
                   "phq_9", "phq_10", "phq_11", "phq_12", 
                   "phq_13", "phq_14", "phq_15")

# Identify spikes and save to a new object
df_spikes_identify <- identidy_spikes(data = df_spikes,
                                      id_var = id, 
                                      repeated_measures = phq_variables, 
                                      cutoff_deterioration = 10, 
                                      cutoff_improvement = 5,
                                      min_between_spike_interval = 9, 
                                      max_spike_duration = 3)

# Print data frame with information about spikes
print(df_spikes_identify)

```
