---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Identify spikes in repeated measures of symptoms

<!-- badges: start -->
<!-- badges: end -->
working on some code for identifying symptom spikes with Asha


## Installation

``` r
# install.packages("devtools")
devtools::install_github("milanwiedemann/spike")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(spike)
```

# Test rename variables function

```{r}

# create list with variables
phq_variables <- c("phq_1", "phq_2", "phq_3", "phq_4", 
                   "phq_5", "phq_6", "phq_7", "phq_8", 
                   "phq_9", "phq_10", "phq_11", "phq_12", 
                   "phq_13", "phq_14", "phq_15")


rename_spike_vars(df_spikes, phq_variables)
```


```{r}
# create list with variables
phq_variables_bad <- c("phqone", "ph2q", "phq3", "phq_four", 
                       "PQH_5", "pHq_6", "phq_7", "phQ8", 
                       "phnine", "phq_100", "phq_1q1", 
                       "phq12", "phq_13", "phq_t14", "phq_s15")

rename_spike_vars(df_spikes_bad, phq_variables_bad)
```

# Test identify spikes with good variable names


```{r}

# identify spikes
identidy_spikes(data = df_spikes,
                id_var = id, 
                # list of repeated measures
                repeated_measures = phq_variables, 
                cutoff_deterioration = 10, 
                cutoff_improvement = 5,
                # Minimum number of sessions between multiple spikes experiences by the same participant
                min_between_spike_interval = 9, 
                # Maximum number of repeated measures between symptom deterioration and improvement 
                # that would still be considered a spike
                max_spike_duration = 10
                ) %>% 
  print(n = 100)

```


# Test identify spikes with bad variable names

```{r}

# identify spikes
identidy_spikes(data = df_spikes_bad,
                id_var = id, 
                # list of repeated measures
                repeated_measures = phq_variables_bad, 
                cutoff_deterioration = 10, 
                cutoff_improvement = 5,
                # Minimum number of sessions between multiple spikes experiences by the same participant
                min_between_spike_interval = 9, 
                # Maximum number of repeated measures between symptom deterioration and improvement 
                # that would still be considered a spike
                max_spike_duration = 10
                ) %>% 
  print(n = 100)

```

# TODOs

- add references
- decide which direction to go to with this
